Artificial Immune based Bot for planetWar game

### 2018-02-28 article.tex
Title and Affiliation changed

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Contribution of computational intelligence tools \\ in the improvement of strategy games}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Mohamed Amine Chikh Touami}
\IEEEauthorblockA{exact science Departement \\
University Mustapha Stembouli\\
Mascara, Algeria\\
Email: ma\_chikhtouhami@hotmail.com}
\and
\IEEEauthorblockN{Homer Simpson}
\IEEEauthorblockA{Twentieth Century Fox\\
Springfield, USA\\
Email: homer@thesimpsons.com}
\and
\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
\IEEEauthorblockA{Starfleet Academy\\
San Francisco, California 96678--2391\\
Telephone: (800) 555--1212\\
Fax: (888) 555--1212}}

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Artificial Immune based Bot for planetWar game}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Mohamed Amine Chikh Touami\\ and SALEM Mohammed}
\IEEEauthorblockA{Faculty of Exact Sciences,\\
University Mustapha Stembouli\\
Mascara, Algeria\\
Email: ma\_chikhtouhami@hotmail.com}
\and
%\IEEEauthorblockN{SALEM Mohammed}
%\IEEEauthorblockA{Faculty of Exact Sciences,\\
%	University Mustapha Stembouli\\
%	Mascara, Algeria\\
%	Email: salem@univ-mascara.dz}
%\and
\IEEEauthorblockN{KHELFI Mohammed Faycal}
\IEEEauthorblockA{RIIR Lab\\
University of Oran 1, Ahmed Ben Bella, Oran, Algeria\\
Email: mf\_khelfi@yahoo.fr}
}
